\documentclass{article}
\input{../../packagesMemoir}
\input{../../macros}

\title{samshodhana-samvAdaM.}
% \date{}
% \author{vishvAs vAsuki}
% htlatex record.tex "tex2html4ht,charset=utf-8" "-cunihtf -utf8"
\begin{document}
\maketitle

\part{Things done since last report}
Presented the affiliation networks paper to others, solicited ideas. But more promising social-nework research topics have emerged apart from graph generation.

I have been reading papers related to these problems, acquired some data-sets, and making further plans for experimentation and pursuing these ideas. Read these papers: 'Co-clustering documents and words using bipartitite spectral graph partitioning: Dhillon' and 'Clustering social networks: Trajan et al'. In one case, failed to get un-anonymized orkut data from authors.

\section{Summary of research activities so far}
Main activities have been: I studied the various temporal/ static, macro/ micro-scopic properties of network evolution. Then, I read about various network evolution models, their merits and demerits. Affilitation networks seem to be attracting much attention lately. From this context, it seems best to divert research towards exploring them (eg: co-clustering them) and their use in solving various problems in social network analysis (eg: in link prediction).

\part{Ideas and questions}
\section{vartamAna-somshodhanAni}
\subsection{Link prediction}
Use microscopic evolution model here; or observe link formation statistics (degree distribution of new linkers etc..) and try to replicate these statistics while making predictions.

credits: \verb jhe~Ngdo~Ng .

\subsubsection{Using affiliation networks}
See if affiliation nw can be used to predict links. Maybe bias assigned to affiliation nw observations can be learned from using the corresponding social-nw evolution data.

credits: \verb jhe~Ngdo~Ng , pratIka.

\subsubsection{Experiments}
Acquire data for evolving social networks, with corresponding affiliation networks. Perhaps Yin Zhang's students are trawling various social networking websites.


\subsection{Partitioning/ clustering bi-partite graphs}
Extend current graph partitioning algorithms to have soft clusters.

Try extending clustering algorithms by Brian and Trajan to co-cluster bi-partitite graphs.

credits: pratIka.

\subsection{Co-Clustering affiliation networks}
credits: pratIka.

\subsubsection{Ideas}
\begin{itemize}
 \item Use special properties of these networks to improve clustering.
 \item Try to use information from corresponding social network to better cocluster the affiliation nw.
\end{itemize}

\subsubsection{Actions}
\begin{itemize}
 \item Acquire affilation network data to experiment with: ones with community names.
 \item Consider previous work on co-clustering bipartite graphs.
 \item Consider previous work on clustering social networks in general. May give you ideas.
\end{itemize}

\subsubsection{Experiments}
\begin{itemize}
 \item Try implementing the simple dhillon alg.
 \item Try applying the Trajan algorithm.
 \item Try the algorithm where ye cluster users and clusters by iteratively folding the affiliation nw to get user nw/ community nw and then using clusters in one nw to cluster the other nw.
\end{itemize}

\subsection{Clustering nodes in social networks}
Cluster nodes in social networks. Use special properties of these networks to improve clustering. Try to use affiliation nw here.

credits: pratIka.

\section{Deferred research projects}
Construct a graph generative model which, besides having good static and temporal properties displayed by graphs evolved using other models, also shows hierarchical community structure.

\begin{itemize}
\item Can you extend the affiliation networks model to do this?
\item This can be done if the idea to use affiliation networks algorithm to generate clusters and then interconnect them works.
\end{itemize}

Given the k*k q(xhat, yhat) matrix, which specifies the edge densities between various node clusters, make a generative model which produces graphs with that clustering structure, such that it possesses various static and temporal properties of real world graphs.

\begin{itemize}
\item A trivial solution exists if the diagonal entries heavily dominate others. Is this well motivated?
\end{itemize}

Consider the problem of learning a decision tree with a 1/n correlated parity, given a noisy parity learner which only works with constant noise.

\part{Suggested Plans}
\section{Administrativia}
Take research course with Prof. Dhillon in fall.

\section{Research}
Pursue ideas and experimentation related to the use of affiliation networks in link prediction, and to the problem of co-clustering affiliation networks.

\subsection{Data acquisition}
Current data we have lacks group names: this makes it hard to evaluate clustering. Trying to get data with group names.

Get data for evolving social networks' snapshots with corresponding affiliation networks.

\section{Feedback}
Indrajita-AchArya mentioned a few papers which presented work related to co-clustering affiliation networks.

He acquiesced to our current lines of research in exploring link prediction and in co-clustering affiliation networks. He suggested that this can be my course-project, but in the meantime I must implement my ideas regarding generation of graphs with a particular cluster structure.

I was reprimanded for not implementing the above algorithm. My concern that there was insufficient motivation/ merit in executing this work was dismissed. My objection to the expectation for my implementing the algorithm on the grounds that it was not initially clear that I was to implement this was also dismissed.

The research course form was signed.

\part{Lessons and plan ahead}
\section{Criticism of the exchange}
The professor, in insisting on my implementing the graph generation algorithm rather than immediately start work on the proposed new projects, and in doing so sternly, is clearly asserting his power over me.

I was nervous. I was unable to understand details in a certain technical conversation. This lapse was recognized.

Nervousness also prevented me from presenting the graph generation algorithm properly. I later wrote it out and showed it, after attempting analysis with pratIka.

During a later conversation, my lack of critical thinking was observed. I was unable to recall the shortcomings of the Kronecker product model and the microscopic network evolution model. On later thought, the latter is not ameanable to mathematical analysis, while the former does not grow one node at a time.

Nervousness should have been overcome by solemnly recognizing that exchange of information/ expectations is the most important point of the meeting and determinedly focusing the intellect on it.

\section{Action required}
Alter communication strategy to eliminate nervousness in future meetings.

Promptly and quickly implement the algorithm and focus on important research.

Update new information about the professor in advisor hunt.
\end{document}

